# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
```{r}
data <- read.csv("/Users/xiangjiang/Documents/git/RepData_PeerAssessment1/activity.csv")
```

## What is mean total number of steps taken per day?
### Make a histogram of the total number of steps taken each day
```{r}
library(ggplot2)
## Using tapply to calculate sum steps per day
steps <- tapply(data$steps, data$date, sum)
dfsteps <- data.frame(names(steps), steps,row.names = NULL)
names(dfsteps) <- c("date", "stepnum")
## Using qplot to plot histogram
qplot(stepnum, data=dfsteps,geom="histogram",binwidth = 300)
```
### Calculate and report the mean and median total number of steps taken per day
Mean steps taken per day:
```{r}
mean(steps, na.rm = TRUE)
```

Median steps taken per day:
```{r}
median(steps, na.rm = TRUE)
```

## What is the average daily activity pattern?
Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
timeseries <- tapply(data$steps, data$interval, mean, na.rm = TRUE)
dftimeseries <- data.frame(names(timeseries), timeseries,row.names = NULL)
names(dftimeseries) <- c("interval", "stepnum")
plot(data$interval[1:288], dftimeseries$stepnum, type="l")
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
The max number of steps are:
```{r}
max(dftimeseries$stepnum)
```
The interval for the max steps are:
```{r}
a<-which.max(dftimeseries$stepnum)
names(a)
```
## Imputing missing values
Calculate and report the total number of missing values in the dataset
The total number of missing values are:
```{r}
length(data$steps[is.na(data$steps)])
```

Devise a strategy for filling in all of the missing values in the dataset.
Replace missing value with mean steps per interval.
```{r}
## replace missing value with mean steps per interval
data$steps[is.na(data$steps)] <- dftimeseries$stepnum[as.character(data$interval[is.na(data$steps)])]
```
Create a new dataset that is equal to the original dataset but with the missing data filled in.
```{r}
newdata <- data
```
Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day.
```{r}
## Using tapply to calculate sum steps per day
steps <- tapply(newdata$steps, data$date, sum)
dfsteps <- data.frame(names(steps), steps,row.names = NULL)
names(dfsteps) <- c("date", "stepnum")
## Using qplot to plot histogram
qplot(stepnum, data=dfsteps,geom="histogram",binwidth = 300)
```
These values differ from the estimates from the first part of the assignment.
Imputing missing data helps fill in the missing values which are treated to be 0 previously,
it helps get a more accurate total daily number of steps.
## Are there differences in activity patterns between weekdays and weekends?
